### 2020-06-05 report/sections/server/node/runtime.tex
Report: complete chapter 4

wss.addEventListener('connection', ws => {
	ws.onmessage = onSubscribe; (*@\label{line:wslisteneroverride}@*)
});
\end{lstlisting}
\captionof{lstlisting}{\dots}
\label{lst:nodeconnect}
\end{figure}

@@

\begin{enumerate}
\item
The server keeps track of the participants that 
have yet to join the session -- this is initialised to the
complete set of
non-server endpoints at the start (\cref{line:initrolesocket}).

@@

\item
Otherwise, the role is not occupied, so the server binds
the WebSocket (which the message was received from) to the role
(\cref{line:connectwsbind}).
This is accumulated in an interface type mapping each
role to an \textit{optional}\footnote{
TypeScript provides utility types for common type transformations:
\texttt{Partial<T>} constructs a type with all properties
of \texttt{T} set to optional.
} 
WebSocket property
-- for roles who have
not yet connected, we do not know the WebSocket binding, so the
WebSocket for these roles are \lstonelinejs{undefined}.

>>>>

wss.addEventListener('connection', ws => {
	ws.onmessage = onSubscribe; (*@\label{line:wslisteneroverride}@*)
});
\end{lstlisting}
\captionof{lstlisting}{Handling Connections in Server Endpoint}
\label{lst:nodeconnect}
\end{figure}

@@

\begin{enumerate}
\item
The server keeps track of the participants that 
have yet to join the session -- this is initialised to the
complete set of
non-server endpoints at the start (\cref{line:initwaiting}).

@@

\item
Otherwise, the role is not occupied, so the server binds
the WebSocket (which the message was received from) to the role
(\cref{line:connectwsbind}).
This is accumulated in an interface type, mapping each
role to an \textit{optional}\footnote{
TypeScript provides utility types for common type transformations:
\texttt{Partial<T>} constructs a type with all properties
of \texttt{T} set to optional.
} 
WebSocket property
-- for roles who have
not yet connected, we do not know the WebSocket binding, so the
WebSocket for these roles are \lstonelinejs{undefined},
as initialised at the start (\cref{line:initroletosocket}).
